---
title: "Analysis of Women Dataset"
author: "Sharon Shabu"
date: "07/22/24"
output: html_notebook
  
Is it possible to predict the weight of a woman using linear regression based on her height?

To analyze the relationship between the height and weight by developing a linear regression model.

The data set used for the following model is "women", which contains the height(inches) and weight(lbs) of women aged 30-39 in America.

1. Loading the libraries in order to load the dataset.
```{r}
library(datasets)
library(ggplot2)
library(caret)
```
2. Loading the dataset.
```{r}
data("women")
```
3. Check for any missing values.
```{r}
missing_values <- sum(is.na(women))
print(missing_values)
```
4. Calculating the correlation.
```{r}
correlation <- cor(women$height, women$weight)
print(correlation)
```
5. The data from the dataset summarized.
```{r}
summary(women)
```
6. Calculating median height and weight.
```{r}
median_height <- median(women$height)
print(paste("Median Height:", median_height))

median_weight <- median(women$weight)
print(paste("Median Weight:", median_weight))
```
7. Creating a scatterplot(Bivariate), I am using a scatterplot as its only two variables that we are analyzing.
```{r}
 plot(women$height, women$weight,
      main = "Height VS Weight",
      xlab = "Height ('')",
      ylab = "Weight (lbs)",
      col = "lightpink")
```
8. Creating the linear regression model, I am using this approach as it is a suitable way to visualize the relationship between these two variables.
```{r}
model <- lm(weight ~ height, data = women)
summary(model)
```
9. The results from the model.
```{r}
print("Results:")
print(coef(model))
```
10. Creating the visualization of the linear regression model.
```{r}
abline(model, col= "green")
```
11. Preparing for cross validation which will help confirm the validity of the predictions.
```{r}
train_control <- trainControl(method = "cv",
                             number= 10)
```
12. Linear regression with cross validation.
```{r}
model_cv <- train(weight ~ height, 
                  data = women,
                  method = "lm",
                  trControl =
                  train_control,
                  metric = "RMSE")  
```
13. Picking the succesful model from the cross validation, and printing its coefficients.
```{r}
print(model_cv)
best_model <- model_cv$finalModel
coefficients <- coef(best_model)
print(coefficients)
```
14. Making a prediction, in this case I will use 61.5 inches for the height.
```{r}
new_height <- 61.5
predicted_weight <- predict(best_model, newdata = data.frame(height = new_height))
print(paste("The predicted weight", new_height, ":", predicted_weight))
```